Hybrid oddball - SSVEP BCI

### 2013-05-22 draftHybridPaper/draftHybridBCI.tex
getting ready for 2 stim experiment

\acrodef{SSVEP}{Steady-State Visually Evoked Potential}
\acrodef{BCI}{Brain-Computer Interface}
\acrodef{ERP}{Event Related Potential}
\acrodef{SVM}{Support Vector Machine}

@@

% General BCI

% P3 BCI, definition, plus and minus

% SSVEP BCI, definition, plus and minus

@@

        % exp description
        As shown in \autoref{fig:stimSeq}, a typical \emph{stimulation cycle}, started with a \SI{2000}{\ms} cue, indicating the participant his/her target item, followed by a \SI{1000}{\ms} pause during which the cue disappears and all icons remained gray.
        The background rectangle then started to flicker and the oddball stimulation started \SI{500}{\ms} later.
        The oddball stimulation consisted of 10~\emph{flashing sequences} during which each of the 6~icons was flashed one after another in random order for a duration randomly set between \SIlist[list-units = single]{200;300}{\ms}.
        As usually done for oddball experiments, the participants were instructed to focus on their target symbol and count the number of time it flashes.
        A \SI{1000}{\ms} pause followed the oddball stimulation and preceded the next cue.
        An \emph{experimental run} lasted approximately 4~minutes and consisted of 12 consecutive stimulation cycles, so that each of the 6~icons was cued twice (in random order).

>>>>

\acrodef{SSVEP}{Steady-State Visually Evoked Potential}
\acrodef{BCI}{Brain-Computer Interface}
\acrodef{ERP}{Event Related Potential}
\acrodef{SVM}{Support Vector Machine}
\acrodef{EEG}{electroencephalography}

@@

% General BCI
\acp{BCI} aim at decoding the brain activity in order to provide a direct communication channel between the brain and an external device.
In this study, the brain activity is recorded using \ac{EEG}, which offer the advantage over other method (\emph{e.g.} micro electrodes, fMRI \ldots) to be non-invasive and easy to set up.

% P3 BCI, definition, plus and minus
Some of the earliest \ac{EEG}-\ac{BCI} systems were based on the P3 component of the \ac{ERP} (\cite{Farwell1988, Donchin2000}).
The P3 is a positive deflection in the EEG time-locked to salient stimuli presented in an oddball paradigm, typically evoked over the parietal cortex, and occurs between \SIlist[list-units = single]{200;500}{\ms} after stimulus onset \cite{Sutton1965}.
Although those \acp{BCI} rely mostly on the P3 component, other components (\emph{e.g.}, occipital N1 and/or N200) may also be used for ERP detection \cite{Bianchi2010, Kaufmann2011}, for this reason we prefer here to use the term \emph{oddball-based \acp{BCI}}.

%%%%%%%%%%%%%%%%%%%%%%%%%%%% pluses and minuses %%%%%%%%%%%%%%%

% SSVEP BCI, definition, plus and minus
Other systems of interest are \acp{BCI} based on \acp{SSVEP}.
They rely on the psychophysiological properties of the EEG brain responses recorded from the occipital cortex during the periodic presentation of identical visual stimuli (\emph{i.e.} flickering stimuli).
When the periodic presentation is at a sufficiently high rate (\SI{>6}{\Hz}), stable and synchronized neural oscillations at the stimulus frequency and its harmonics are evoked over the visual cortex \cite{Regan1966, Herrmann2001, Luck2005}.
Such \acp{BCI} are particularly attractive because \acp{SSVEP} have high signal-to-noise ratios and are less susceptible to eye movement and blink artifacts \cite{Perlstein2003} as well as electromyographic artifacts \cite{Gray2003}.
Several \ac{SSVEP}-based \acp{BCI} have been successfully tested with healthy subjects (see \cite{Vialatte2010} for a review).

%%%%%%%%%%%%%%%%%%%%%%%%%%%% pluses and minuses %%%%%%%%%%%%%%%

@@

        % exp description
        As shown in \autoref{fig:stimSeq}, a typical \emph{stimulation cycle}, starts with a \SI{2000}{\ms} cue, indicating the participant his/her target item, followed by a \SI{1000}{\ms} pause during which the cue disappears and all icons remained gray.
        The background rectangle starts then to flicker and the oddball stimulation begins \SI{500}{\ms} later.
        The oddball stimulation consisted of 10~\emph{flashing sequences} during which each of the 6~icons was flashed one after another in random order for a duration randomly set between \SIlist[list-units = single]{200;300}{\ms}.
        As usually done for oddball experiments, the participants were instructed to focus on their target symbol and count the number of time it flashes.
        A \SI{1000}{\ms} pause followed the oddball stimulation and preceded the next cue.
        An \emph{experimental run} lasted approximately 4~minutes and consisted of 12 consecutive stimulation cycles, so that each of the 6~icons was cued twice (in random order).
